% !TEX root = ../TechProject.tex

\graphicspath{{Chapter1/}}

% for example

\chapter{Introduction}
With the rise of streaming services for multiple formats, one interacts with recommendation systems daily. For music streaming, its an ideal way of filtering the sheer quantity of commercially available music down to an amount that aligns well with ones taste. The prevalence of machine learning has led to this technology being leveraged by streaming services such as Spotify \citep{httpsresearchatspotifycommachine-learning_machine_2023}. For the majority of listeners automating the discovery process has been well received however a subset of listeners still find these systems inadequate.

Recent studies have highlighted that people with objectively "diverse" music tastes usually rely on non algorithmic ways of finding music \citep{anderson_algorithmic_2020}. This is apparent in the continuing popularity of internet radio and services like Bandcamp \citep{market_research_future_internet_2022} \citep{roberts_anti-spotify_2020}. 

DJs are a type of user who fall in the category of having a diverse taste. In preparing a DJ set, DJs often source music in non algorithmic ways \citep{allen_djs_2021}.

 The sheer quantity of DJ sets now on the internet raises the possibility that this data could be used to train a recommendation system that would provide an effective, algorithmic way for suggesting music to this specific audience. This paper presents a recommendation system application trained on DJ sets, and compares it's recommendation performance with top performing models.

This paper explores:

\begin{enumerate}
	\item \textit{What are effective methods for the automated recommendation of songs suitable for adding to a given DJ set?}
	\item \textit{Is the proposed method a suitable solution for the automated recommendation of songs suitable for adding to a given DJ set?}
	\item \textit{Can a DJ-set centric dataset be used to solve other DJ tasks?}
\end{enumerate}

Chapter 2 and 3 cover a literature review. Chapter 4 presents gaps in current studies, and provides an hypothesis for how these gaps could be addressed. Chapter 5 gives an overview of the application and describes example recommendations. Chapter 6 runs through the method of evaluating the application's recommendations. Chapter 7 compares the results found to industry standard models. Chapter 8 concludes the study and discusses further work.
 