%%% PREAMBLE
\documentclass[11pt,titlepage,oneside]{book}
\usepackage{tablefootnote}
\usepackage{float}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper}

%%%%%% FOR TESTING ONLY %%%%%%%%%%%%%
\usepackage[english]{babel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%

\usepackage{graphicx} % enhanced grpahics support
\renewcommand{\sfdefault}{cmbr} % slightly nicer than the standard sans serif font
\usepackage[onehalfspacing]{setspace} % line spacing
\usepackage[T1]{fontenc} % font encoding (fixes some font-related errors)
\usepackage{textcomp} % more font encoding
\usepackage[printonlyused]{acronym} % To handle acronyms
\usepackage{appendix} % For managing appendices (makes ToC neater)
\usepackage{fancyref}

%%%%%%%%%%%%%%%%% DOCUMENT PROPERTIES %%%%%%%%%%%%%%%%%

% Thesis details
\newcommand{\LongTitle}{Collaborative-Based Filtering Music Recommendation System for DJ Sets}
\newcommand{\Me}{Harvey James Prewer}

% Number of document levels
\setcounter{secnumdepth}{4}

% Prevent hyphenation
\hyphenpenalty=5000
\tolerance=1000

%%%%%%%%%%%%%%%%% ACRONYMS AND SYMBOLS %%%%%%%%%%%%%%%%%

\newcommand{\RT}{RT\ensuremath{_{\text{60}}}}
\newcommand{\DEG}{\ensuremath{^\circ}}

%%%%%%%%%%%%%%%%% DATE %%%%%%%%%%%%%%%%%

% For placing on title page
\usepackage{datetime}
\newdateformat{MyMonth}{\monthname[\THEMONTH]}
\newdateformat{MyYear}{\THEYEAR}
\newdateformat{MyDate}{\THEYEAR}

%%%%%%%%%%%%%%%%% CAPTIONS %%%%%%%%%%%%%%%%%

\usepackage[margin=2em,singlelinecheck=on,font=sf,labelfont+=bf,labelformat=simple,labelsep=colon]{caption}

\newcommand{\captionfontsize}{\fontsize{9}{11}\selectfont}
\renewcommand\captionfont{\captionfontsize\sffamily}

%%%%%%%%%%%%%%%%% TITLES %%%%%%%%%%%%%%%%%

\usepackage[sf,raggedright,toctitles]{titlesec}

% Chapter heading properties
\titlespacing{name=\chapter}{0ex}{0ex}{.5in}[0ex]
\titlespacing{name=\chapter,numberless}{0ex}{0ex}{.5in}[0ex]

% Subsubsection heading properties
\titleformat{name=\subsubsection,numberless}[hang]{\sf}{}{0pt}{\bfseries}
\titlespacing{name=\subsubsection,numberless}{0em}{2ex}{0ex}

%%%%%%%%%%%%%%%%% TOC / LOF / LOT / LOE %%%%%%%%%%%%%%%%%

\usepackage[titles]{tocloft}

\setcounter{lofdepth}{1}

% put "Chapter #: " in ToC
\renewcommand{\cftchappresnum}{\chaptername~}
\renewcommand{\cftchapaftersnum}{:}
\newlength{\mylen} % a "scratch" length
\settowidth{\mylen}{\bfseries\chaptername\cftchapaftersnum} % extra space
\addtolength{\cftchapnumwidth}{\mylen} % add the extra space

% control indention
\setlength{\cftchapindent}{0em}
\setlength{\cftfigindent}{0em}
\setlength{\cfttabindent}{0em}

\newlength{\tocloftindent}
\setlength{\tocloftindent}{2.3em}

\setlength{\cftsecindent}{1.5em}

%\renewcommand{\@pnumwidth}{1.9em} % was 1.55em
%\renewcommand{\@tocrmarg}{2.9em plus1fil} % raggedright toc entries (no hyphenation)

\setlength{\cftsubsecindent}{3.8em}

%%%%%%%%%%%%%%%%% TABLES %%%%%%%%%%%%%%%%%

\usepackage{array,color,colortbl,multirow,longtable}

\newcommand{\colheading}[1]{\multirow{2}{*}{\textbf{#1}}} % custom column heading command
\newcommand{\tablesubtitle}[2]{\multicolumn{#1}{l}{\emph{#2}}} % custom table sub heading to span the specified number of columns
\renewcommand\arraystretch{1.2} % row height

%%%%%%%%%%%%%%%%% MATHS %%%%%%%%%%%%%%%%%

\usepackage{amsmath,amsbsy,amssymb}

\allowdisplaybreaks

% define new symbols and operators
\newcommand{\R}{\mathfrak{R}} % Real operator
\newcommand{\Z}{\mathbb{Z}} % set of integers
\newcommand{\N}{\mathbb{N}} % set of natural numbers
\newcommand{\F}{\mathcal{F}} % Fourier operator
\newcommand{\ud}{\,\text{d}} % d in differential
\newcommand{\fs}{f\negthinspace{}s} % sampling frequency
\DeclareMathOperator*{\argmax}{arg\,max} % arg min
\DeclareMathOperator*{\argmin}{arg\,min} % arg max
\providecommand{\abs}[1]{\lvert#1\rvert} % abs brackets

%%%%%%%%%%%%%%%%% CITATIONS %%%%%%%%%%%%%%%%%

\usepackage[round]{natbib}

\setcitestyle{aysep={,},notesep={: },citesep={;},yysep={,}}
%\setcitestyle{authoryear,open={(},close={)}}

\setlength{\bibhang}{0pt}

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\newcommand{\citequote}[1]{\newline \strut\hfill \citep{#1}}
\newcommand{\cpage}[1]{p.~#1}
\newcommand{\cpages}[2]{pp.~#1--#2}
\renewcommand\bibname{References}

%%%%%%%%%%%%%%%%% HEADER/FOOTER %%%%%%%%%%%%%%%%%

\usepackage{fancyhdr}
\setlength{\headheight}{15pt}

\newcommand{\myfooter}{\textsf{\thepage}}

\fancypagestyle{plain}{%
	\fancyhf{}%
	\fancyfoot[R]{\myfooter}%
	\renewcommand{\headrulewidth}{0pt}%
	\renewcommand{\footrulewidth}{1pt}%
}

\pagestyle{fancy}
\fancyhf{}%
\renewcommand{\headrulewidth}{1pt} %header line width
\renewcommand{\footrulewidth}{1pt} % footer rule width
\fancyhead[R]{\textsf{\nouppercase{\leftmark}}} % header right - chapter title
\fancyfoot[R]{\myfooter} % footer right - page number

%%%%%%%%%%%%%%%%% HYPERREF %%%%%%%%%%%%%%%%%

% this should hopefully be the last entry in the preamble - defines properties of the typeset pdf file
% this package makes clickable links in the pdf
\usepackage[colorlinks,breaklinks,pdfdisplaydoctitle,plainpages=false]{hyperref} 
\hypersetup{pdftitle={\LongTitle},pdfauthor={\Me},
	citecolor=black,%
	filecolor=black,%
	linkcolor=black,%
	urlcolor=black
}

\renewcommand{\equationautorefname}{Equation}
\renewcommand{\figureautorefname}{Figure}
\renewcommand{\Itemautorefname}{Item}
\renewcommand{\tableautorefname}{Table}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Section}
\renewcommand{\subsubsectionautorefname}{Section}
\renewcommand{\chapterautorefname}{Chapter}
\renewcommand{\partautorefname}{Part}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% DOCUMENT %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	\pdfbookmark[0]{Title page}{title} % Sets a PDF bookmark for the title page
	\setlength{\parindent}{0pt} % set paragraph indent
	\setlength{\parskip}{0ex} % set paragraph spacing
	\pagenumbering{alph} % prevents warnings about duplicated page numbering
	
	\include{FrontMatter/FrontMatter}
	
	%%%%%%%%%%%%%%%%% MAIN %%%%%%%%%%%%%%%%%
	\mainmatter
	
	% change header
	\renewcommand{\chaptermark}[1]{\markboth{\chaptertitlename\ \thechapter: #1}{}}
	
	\pagenumbering{arabic}
	\setlength\abovedisplayshortskip{0.5\baselineskip}
	\setlength\belowdisplayshortskip{0.5\baselineskip}
	\setlength\abovedisplayskip{0.5\baselineskip}
	\setlength\belowdisplayskip{0.5\baselineskip}
	
	%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%
	% For example
	
	%\include{Introduction}
	
	% The argument for \include is a filename of a LaTeX file contained within the same folder at this file. It could also be placed in a subfolder; the argument can then be specified as {subfolder_name/filename}.
	
	% The \include'd file contains LaTeX commands that will, more or less, be read as if the code was contained in this file at the point the \include was called.
	
	% There is an equivalent command, \includeonly, which you should place at the top of your document. Use this command to choose the files to include (rather than commenting lines). In this way, the document will be typeset as if the files were present (so links and cross-references won't be broken), but any output associated with the files will be excluded.
	
	% Another tip: If using TeXShop, which uses synctex, you can command click on the preview to find the corresponding commands in your source. The reverse operation is also permitted. To do this from \include'd files, you need to tell TeXShop what the root file is. This is done by placing this line AT THE TOP of each \include'd file (you must include the "%"):
	% ! TEX root = root_filename.tex
	% Doing this has other advantages, like being able to typeset from an included file, rather than having to typeset from the root file.

% Chapter 1
\include{Chapter1/Chapter1}

% Chapter 2
\include{Chapter2/Chapter2}

% Chapter 3
\include{Chapter3/Chapter3}

% Chapter 4
\include{Chapter4/Chapter4}

% Chapter 5
\include{Chapter5/Chapter5}

% Chapter 6
\include{Chapter6/Chapter6}

% Chapter 7
\include{Chapter7/Chapter7}

% Chapter 7
\include{Chapter8/Chapter8}

%% Appendices
%% appendices work in an identical way to chapters (in terms of syntax), but are labelled alphabetically rather than numerically
\appendix
% Replace "Chapter" with "Appendix"
\addtocontents{toc}{\protect\renewcommand{\protect\cftchappresnum}{\appendixname~}}
\addtocontents{toc}{\protect\addtolength{\cftchapnumwidth}{1em}}
%\input{Appendix1}
%\input{Appendix2}

% Last I checked, the Appendix and Titlesec package do not get on with each other. So use "input" for appendix chapters instead. If you still want to use \includeonly, put the \input commands in another file and \include that.

%%%%%%%%%%%%%%%%% BACK MATTER %%%%%%%%%%%%%%%%%
\backmatter

% header
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\include{BackMatter/BackMatter}

%\bibliography{BackgroundReading.bib}

\begin{thebibliography}{97}
	\newcommand{\enquote}[1]{\textit{#1}}
	\providecommand{\natexlab}[1]{#1}
	\providecommand{\url}[1]{\texttt{#1}}
	\providecommand{\urlprefix}{Available at: }
	\expandafter\ifx\csname urlstyle\endcsname\relax
	\providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
	\providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
		\urlstyle{rm}\Url}\fi
	
	\bibitem[{AIcrowd(2023)}]{aicrowd_aicrowd_2023}
	AIcrowd (2023): \enquote{{AIcrowd} {\textbar} {Spotify} {Million} {Playlist}
		{Dataset} {Challenge} {\textbar} {Challenges}},
	\urlprefix\url{https://www.aicrowd.com/challenges/spotify-million-playlist-dataset-challenge} (Accessed: 20th March 2023).
	
	\bibitem[{Allen(2021)}]{allen_djs_2021}
	Allen, T. (2021): \enquote{{DJs} and the lost art of 'digging'},
	\urlprefix\url{https://www.mrafterparty.com/djs-and-the-lost-art-of-digging/} (Accessed: 20th March 2023).
	
	\bibitem[{Anderson et~al.(2020)Anderson, Maystre, Anderson, Mehrotra, and
		Lalmas}]{anderson_algorithmic_2020}
	Anderson, A., Maystre, L., Anderson, I., Mehrotra, R., and Lalmas, M. (2020):
	'Algorithmic {Effects} on the {Diversity} of {Consumption} on
		{Spotify}', in \textit{Proceedings of {The} {Web} {Conference} 2020}, Taipei,
	Taiwan, April 2020. pp. 2155-2165. \doi{10.1145/3366423.3380281}.
	
	\bibitem[{Anderson et~al.(2003)Anderson, Ball, Boley, Greene, Howse, Lemire,
		and McGrath}]{anderson_racofi_2003}
	Anderson, M., Ball, M., Boley, H., Greene, S., Howse, N., Lemire, D., and
	McGrath, S. (2003): '{RACOFI}: {A} {Rule}-{Applying} {Collaborative}
		{Filtering} {System}', in \textit{International Workshop on Collaboration Agents: Autonomous Agents for Collaborative Environments}, Nova Scotia, Canada, 2003. pp. 53-72.
	
	\bibitem[{Aucouturier et~al.(2002)Aucouturier, Pachet, and
		{others}}]{aucouturier_music_2002}
	Aucouturier, J.-J., Pachet, F., and {others} (2002): \enquote{Music similarity
		measures: {What}'s the use?} in \textit{Ismir 2002}, Paris, 2002. vol.~7, pp.\ignorespaces
	339-340.
	
	\bibitem[{Avery and Zeckhauser(1997)}]{avery_recommender_1997}
	Avery, C. and Zeckhauser, R. (1997): 'Recommender systems for
		evaluating computer messages', \textit{Communications of the ACM}, 40(3),
	pp.\ignorespaces 88--89, \doi{10.1145/245108.245127}.
	
	\bibitem[{Bandcamp(2023)}]{bandcamp_about_2023}
	Bandcamp (2023): \enquote{About {Bandcamp}},
	\urlprefix\url{https://bandcamp.com/about}.
	
	\bibitem[{Barna(2017)}]{barna_perfect_2017}
	Barna, E. (2017): '{The} perfect guide in a crowded musical
		landscape:” {Online} music platforms and curatorship', \textit{First
		Monday} 22(4), \doi{10.5210/fm.v22i4.6914}.
	
	\bibitem[{Bittner et~al.(2017)Bittner, Gu, Hernandez, Humphrey, Jehan, McCurry,
		and Montecchio}]{bittner_automatic_2017}
	Bittner, R.~M., Gu, M., Hernandez, G., Humphrey, E.~J., Jehan, T., McCurry,
	P.~H., and Montecchio, N. (2017): 'Automatic playlist sequencing and
		transitions', in \textit{Proc. International Society for Music Information Retrieval Conference (ISMIR)}, Suzhou, China, October 23-27
		2017. pp. 442-448.
	
	\bibitem[{Bollen et~al.(2010)Bollen, Knijnenburg, Willemsen, and
		Graus}]{bollen_understanding_2010}
	Bollen, D., Knijnenburg, B.~P., Willemsen, M.~C., and Graus, M. (2010):
	'Understanding choice overload in recommender systems', \textit{In Proceedings of the fourth ACM conference on Recommender systems.} Barcelona, Spain, September 26-30, 2010. pp. 63-70. \doi{10.1145/1864708.1864724}.
	
	\bibitem[{Bourdieu and Nice(2010)}]{bourdieu_distinction_2010}
	Bourdieu, P. and Nice, R. (2010): \textit{Distinction: {A} {Social} {Critique}
		of the {Judgement} of {Taste}}. London: Taylor \& Francis
	Group.
	
	\bibitem[{Brewster and Broughton(2014)}]{brewster_last_2014}
	Brewster, B. and Broughton, F. (2014): \textit{Last {Night} a {DJ} {Saved} {My}
		{Life}: {The} {History} of the {Disc} {Jockey}}, London: Headline.
	
	\bibitem[{Böck and Davies(2020)}]{bock_deconstruct_2020}
	Böck, S. and Davies, M. E.~P. (2020): 'Deconstruct, Analyse, Reconstruct: How to improve Tempo, Beat, and Downbeat Estimation', in \textit{Proceedings of the 21st International Society for Music Information Retrieval Conference,} Montreal, QC, Canada, 12–16 October 2020. pp. 574-592.
	
	\bibitem[{Böck et~al.(2019)Böck, Davies, and Knees}]{bock_multi-task_2019}
	Böck, S., Davies, M. E.~P., and Knees, P. (2019): 'Multi-Task Learning of Tempo and Beat: Learning One to Improve the Other', in \textit{Proc. of the 20th Intl. Society for Music
		Information Retrieval Conf}, Delft, The Netherlands, November 4-8, 2019. pp. 486-493.
	
	\bibitem[{Canuma(2022)}]{canuma_what_2022}
	Canuma, P. (2022): \textit{What Are RBMs, Deep Belief Networks and Why Are They Important to Deep Learning?} Available at: \url{https://medium.com/swlh} 
	(Accessed: 20th March 2023).
	
	\bibitem[{Casey et~al.(2008)Casey, Veltkamp, Goto, Leman, Rhodes, and
		Slaney}]{casey_content-based_2008}
	Casey, M.~A., Veltkamp, R., Goto, M., Leman, M., Rhodes, C., and Slaney, M.
	(2008): 'Content-{Based} {Music} {Information} {Retrieval}: {Current}
		{Directions} and {Future} {Challenges}', in \textit{Proceedings of the IEEE},
	vol. 96(4), pp.\ignorespaces 668--696, \doi{10.1109/JPROC.2008.916370}. 
	
	\bibitem[{Celma(2010{\natexlab{a}})}]{celma_music_2010}
	Celma, O. (2010{\natexlab{a}}): Music Recommendation, in
	O.~Celma (ed.) \textit{Music {Recommendation} and {Discovery}: {The} {Long}
		{Tail}, {Long} {Fail}, and {Long} {Play} in the {Digital} {Music} {Space}},
	Berlin, Heidelberg: Springer, pp.\ignorespaces 43-81,
	\doi{10.1007/978-3-642-13287-2_2}.
	
	\bibitem[{Celma(2010{\natexlab{b}})}]{celma_recommendation_2010}
	Celma, O. (2010{\natexlab{b}}): The {Recommendation} {Problem}, in
	O.~Celma (ed.) \textit{Music {Recommendation} and {Discovery}: {The} {Long}
		{Tail}, {Long} {Fail}, and {Long} {Play} in the {Digital} {Music} {Space}},
	Berlin, Heidelberg: Springer, pp.\ignorespaces 15--41,
	\doi{10.1007/978-3-642-13287-2_2}.
	
	\bibitem[{Chang et~al.(2017)Chang, Huang, and Wu}]{chang_personalized_2017}
	Chang, H.-Y., Huang, S.-C., and Wu, J.-H. (2017): "A personalized music
		recommendation system based on electroencephalography feedback", in
	\textit{Multimedia Tools and Applications}, Volume 76(19), pp.\ignorespaces
	19523--19542, \doi{10.1007/s11042-015-3202-4}.
	
	\bibitem[{Chen et~al.(2022)Chen, Hsu, Liao, Ramírez, Mitsufuji, and
		Yang}]{chen_automatic_2022}
	Chen, B.-Y., Hsu, W.-H., Liao, W.-H., Ramírez, M. A.~M., Mitsufuji, Y., and
	Yang, Y.-H. (2022): "Automatic {DJ} {Transitions} with
		{Differentiable} {Audio} {Effects} and {Generative} {Adversarial}
		{Networks}", in \textit{{ICASSP} 2022 - 2022 {IEEE} {International}
		{Conference} on {Acoustics}, {Speech} and {Signal} {Processing} ({ICASSP})}, Singapore, May 22-27, 2022.
	pp.\ignorespaces 466--470, \doi{10.1109/ICASSP43922.2022.9746663}.
	
	\bibitem[{Chesters(2017)}]{chesters_history_2017}
	Chesters, A. (2017): \enquote{History of the {Pioneer} {CDJs} ({DJ} {CD}
		{Decks}) \& “{Forgotten} {Child}”, the {DMP}-555},
	\urlprefix\url{https://adamch.com/history-of-the-pioneer-cdj/} (Accessed: 20th March 2023).
	
	\bibitem[{Chollet(2017)}]{chollet_xception_2017}
	Chollet, F. (2017): "Xception: {Deep} {Learning} with {Depthwise}
		{Separable} {Convolutions}", in \textit{Proceedings of the IEEE conference on computer vision and pattern recognition}, Honolulu, July 21-26 2017. pp.1251-1258 \doi{10.48550/arXiv.1610.02357}
	
	\bibitem[{Chow(2020)}]{chow_music_2020}
	Chow, D. (2020): \enquote{Music {Recommendation} {System} for {DJs}},
	\urlprefix\url{https://python.plainenglish.io/music-recommendation-system-for-djs-d253d472677e} (Accessed: 20th March 2023).
	
	\bibitem[{Claypool et~al.(1999)Claypool, Gokhale, Miranda, Murnikov, Netes, and
		Sartin}]{claypool_combining_1999}
	Claypool, M., Gokhale, A., Miranda, T., Murnikov, P., Netes, D., and Sartin, M.
	(1999): "Combining {Content}-{Based} and {Collaborative} {Filters} in
		an {Online} {Newspaper}", in \textit{Proc. of Workshop on Recommender Systems-Implementation and Evaluation}, Berkeley, August 19.
	
	\bibitem[{DiMaggio(1987)}]{dimaggio_classification_1987}
	DiMaggio, P. (1987): 'Classification in {Art}', \textit{American
		Sociological Review}, pp.\ignorespaces 440-455
	
	\bibitem[{DMS(2020)}]{dms_apple_2020}
	DMS (2020): \enquote{Apple {Announces} {Apple} {Music} {Radio} {Streaming}
		{Stations}},
	\urlprefix\url{https://deanemediasolutions.com/apple-announces-apple-music-radio-streaming-stations/} (Accessed: 20th March 2023).
	
	\bibitem[{Ferretti(2018)}]{ferretti_clustering_2018}
	Ferretti, S. (2018): "Clustering of {Musical} {Pieces} {Through}
		{Complex} {Networks}: {An} {Assessment} {Over} {Guitar} {Solos}",
	\textit{IEEE MultiMedia}, 25(4), San Diego, July 23-27. pp.\ignorespaces 57--67,
	\doi{10.1109/MMUL.2018.2873497}.
	
	\bibitem[{Ferwerda et~al.(2015)Ferwerda, Schedl, and
		Tkalcic}]{ferwerda_personality_2015}
	Ferwerda, B., Schedl, M., and Tkalcic, M. (2015): "Understanding users' music listening needs", in \textit{Posters, {Demos}, {Late}-breaking {Results} and {Workshop}
		{Proceedings} of the 23rd {Conference} on {User} {Modeling}, {Adaptation},
		and {Personalization} ({UMAP} 2015) {Dublin}, {Ireland}, {June} 29-{July} 3,
		2015}. vol. 1388.
	
	\bibitem[{Dhapte(2022)}]{market_research_future_internet_2022}
	Dhapte, A. (2022): \enquote{Internet {Radio} {Market}},
	\urlprefix\url{https://www.marketresearchfuture.com/reports/internet-radio-market-3892} (Accessed: 20th March 2023).
	
	\bibitem[{George et~al.(2022)George, Mary, and
		George}]{george_development_2022}
	George, A., Mary, X.~A., and George, S.~T. (2022): "Development of an
		intelligent model for musical key estimation using machine learning
		techniques", in \textit{Multimedia Tools and Applications}, 81(14),
	pp.\ignorespaces 19945--19964, \doi{10.1007/s11042-022-12432-y}.
	
	\bibitem[{Gillett(2021)}]{gillett_how_2021}
	Gillett, E. (2021): \enquote{How independent radio has thrived in the pandemic},
	\urlprefix\url{https://djmag.com/longreads/how-independent-radio-has-thrived-pandemic} (Accessed: 20th March 2023).
	
	\bibitem[{Gillhofer and Schedl(2015)}]{gillhofer_iron_2015}
	Gillhofer, M. and Schedl, M. (2015): "Iron {Maiden} {While} {Jogging},
		{Debussy} for {Dinner}?" in \textit{MultiMedia Modeling: 21st International Conference}, Sydney, NSW, Australia, January 5-7, 2015. pp.\ignorespaces
	380--391. \doi{10.1007/978-3-319-14442-9_44}.
	
	\bibitem[{Goldberg et~al.(1992)Goldberg, Nichols, Oki, and
		Terry}]{goldberg_using_1992}
	Goldberg, D., Nichols, D., Oki, B.~M., and Terry, D. (1992): "Using
		collaborative filtering to weave an information tapestry", in
	\textit{Communications of the ACM}, 35(12), pp.\ignorespaces 61--70,
	\doi{10.1145/138859.138867}.
	
	\bibitem[{Han et~al.(2006)Han, Pei, and Kamber}]{han_data_2006}
	Han, J., Pei, J., and Kamber, M. (2006): \textit{Data {Mining}}, Burlington, United States: Elsevier Science \& Technology.
	
	\bibitem[{Hennequin et~al.(2020)Hennequin, Khlif, Voituret, and
		Moussallam}]{hennequin_spleeter_2020}
	Hennequin, R., Khlif, A., Voituret, F., and Moussallam, M. (2020):
	"Spleeter: a fast and efficient music source separation tool with
		pre-trained models", \textit{Journal of Open Source Software}, 5(50),
	p.\ignorespaces 2154, \doi{10.21105/joss.02154}.
	
	\bibitem[{Hofmann(2006)}]{hofmann_support_2006}
	Hofmann, M. (2006): \enquote{Support vector machines-kernels and the kernel
		trick}, \textit{Notes}, 26(3), pp.\ignorespaces 1--16. Publisher: University
	of Bamberg Bamberg, Germany.
	
	\bibitem[{Google(2023)}]{httpsdevelopersgooglecom_matrix_2023}
	Google (2023): \enquote{Matrix {Factorization}
		{\textbar} {Machine} {Learning}},
	\urlprefix\url{https://developers.google.com/machine-learning/recommendation/collaborative/matrix} (Accessed: 20th March 2023).
	
	\bibitem[{Spotify Research(2023)}]{httpsresearchatspotifycommachine-learning_machine_2023}
	Spotify Research (2023): \enquote{Machine
		{Learning}},
	\urlprefix\url{https://research.atspotify.com/machine-learning/} (Accessed: 20th March 2023).
	
	\bibitem[{Isinkaye et~al.(2015)Isinkaye, Folajimi, and
		Ojokoh}]{isinkaye_recommendation_2015}
	Isinkaye, F.~O., Folajimi, Y.~O., and Ojokoh, B.~A. (2015):
	"Recommendation systems: {Principles}, methods and evaluation",
	\textit{Egyptian Informatics Journal}, 16(3), pp.\ignorespaces 261--273,
	\doi{10.1016/j.eij.2015.06.005}.
	
	\bibitem[{Jain et~al.(2020)Jain, Patel, Nagalapatti, Gupta, Mehta, Guttula,
		Mujumdar, Afzal, Sharma~Mittal, and Munigala}]{jain_overview_2020}
	Jain, A., Patel, H., Nagalapatti, L., Gupta, N., Mehta, S., Guttula, S.,
	Mujumdar, S., Afzal, S., Sharma~Mittal, R., and Munigala, V. (2020):
	"Overview and {Importance} of {Data} {Quality} for {Machine}
		{Learning} {Tasks}", in \textit{Proceedings of the 26th {ACM} {SIGKDD}
		{International} {Conference} on {Knowledge} {Discovery} \& {Data} {Mining}},
	Virtual Event CA USA: ACM, pp.\ignorespaces 3561--3562,
	\doi{10.1145/3394486.3406477}.
	
	\bibitem[{Jansson et~al.(2017)Jansson, Humphrey, Montecchio, Bittner, Kumar,
		and Weyde}]{jansson_singing_2017}
	Jansson, A., Humphrey, E., Montecchio, N., Bittner, R., Kumar, A., and Weyde,
	T. (2017): "Singing voice separation with deep {U}-{Net}
		convolutional networks", in \textit{Proc. 18th Int. Soc. Music Inf. Retrieval Conf}., 2017,
		pp. 23–27.
	
	\bibitem[{K et~al.(2006)K, Frankowski, and Riedl}]{k_you_2006}
	K, S., Frankowski, D., and Riedl, J. (2006): "Do {You} {Trust} {Your}
		{Recommendations}? {An} {Exploration} of {Security} and {Privacy} {Issues} in
		{Recommender} {Systems}", in \textit{Emerging Trends in Information and Communication Security: International Conference}, ETRICS 2006, Freiburg, Germany, June 6-9, 2006. Proceedings (pp. 14-29). Springer Berlin Heidelberg.,
	\doi{10.1007/11766155_2}.
	
	\bibitem[{!K7(2023)}]{k7_about_2023}
	!K7 (2023): \enquote{About}, \urlprefix\url{https://k7.com/about/} (Accessed: 20th March 2023).
	
	\bibitem[{Kaminskas et~al.(2013)Kaminskas, Ricci, and
		Schedl}]{kaminskas_location-aware_2013}
	Kaminskas, M., Ricci, F., and Schedl, M. (2013): "Location-aware music
		recommendation using auto-tagging and hybrid matching", in
	\textit{Proceedings of the 7th {ACM} conference on {Recommender} systems},
	{RecSys} '13, New York, NY, USA: Association for Computing Machinery,
	pp.\ignorespaces 17--24, \doi{10.1145/2507157.2507180}.
	
	\bibitem[{Kim et~al.(2017)Kim, Park, Park, Ha, Kwon, and
		Nam}]{kim_automatic_2017}
	Kim, A., Park, S., Park, J., Ha, J.-W., Kwon, T., and Nam, J. (2017):
	"Automatic {DJ} {Mix} {Generation} {Using} {Highlight} {Detection}", in \textit{Proc. ISMIR, late-breaking demo paper.}
	
	\bibitem[{Kim et~al.(2022)Kim, Yang, and Nam}]{kim_joint_2022}
	Kim, T., Yang, Y.-H., and Nam, J. (2022): "Joint {Estimation} of
		{Fader} and {Equalizer} {Gains} of {DJ} {Mixers} {Using} {Convex}
		{Optimization}", in \textit{25th International Conference on Digital Audio Effects}, Vienna, Austria, September 6-10 2022. pp. 312-319.
	
	\bibitem[{Kirn(2023)}]{kirn_review_2023}
	Kirn, P. (2023): \enquote{In {Review}: {Serato} {Stems} · {Feature} {RA}},
	\urlprefix\url{https://ra.co/features/4105} (Accessed: 20th March 2023).
	
	\bibitem[{Koren et~al.(2009)Koren, Bell, and Volinsky}]{koren_matrix_2009}
	Koren, Y., Bell, R., and Volinsky, C. (2009): "Matrix {Factorization}
		{Techniques} for {Recommender} {Systems}", \textit{Computer}, 42(8),
	pp.\ignorespaces 30--37. \doi{10.1109/MC.2009.263}
	
	\bibitem[{Kumaraswamy(2022)}]{kumaraswamy_optimal_2022}
	Kumaraswamy, B. (2022): "Optimal classification of music genres based
		on acoustic and visual features", \textit{Concurrency and Computation:
		Practice and Experience}, 34(23), p.\ignorespaces e7174,
	\doi{10.1002/cpe.7174}. 
	
	\bibitem[{Laplante(2014)}]{laplante_improving_2014}
	Laplante, A. (2014): "Improving music recommender systems: What can we learn from research on music tastes?", in \textit{ISMIR}. pp. 451-456.
	
	\bibitem[{Lea et~al.(2017)Lea, Flynn, Vidal, Reiter, and
		Hager}]{lea_temporal_2017}
	Lea, C., Flynn, M.~D., Vidal, R., Reiter, A., and Hager, G.~D. (2017):
	"Temporal {Convolutional} {Networks} for {Action} {Segmentation} and
		{Detection}", in \textit{2017 {IEEE} {Conference} on {Computer} {Vision} and
		{Pattern} {Recognition} ({CVPR})}, Honolulu, July 21-26 2017. pp.\ignorespaces
	1003--1012. \doi{10.1109/CVPR.2017.113}.
	
	\bibitem[{Lemire and Maclachlan(2007)}]{lemire_slope_2007}
	Lemire, D. and Maclachlan, A. (2007): "Slope {One} {Predictors} for
		{Online} {Rating}-{Based} {Collaborative} {Filtering}", in \textit{Proceedings
		of the 2005 SIAM International Conference on Data Mining}. pp. 371-475.
	\doi{10.1137/1.9781611972757.43}.
	
	\bibitem[{Logan(2004)}]{logan_music_2004}
	Logan, B. (2004): "Music {Recommendation} from {Song} {Sets}", in \textit{ISMIR}. pp. 425-428 .
	
	\bibitem[{McFee and Lanckriet(2012)}]{mcfee_hypergraph_2012}
	McFee, B. and Lanckriet, G. (2012): "Hypergraph models of playlist dialects", in \textit{ISMIR}. pp. 343-348
	
	\bibitem[{Mirjalili and Lewis(2016)}]{mirjalili_whale_2016}
	Mirjalili, S. and Lewis, A. (2016): "The {Whale} {Optimization}
		{Algorithm}", in \textit{Advances in Engineering Software}, 95, pp.\ignorespaces
	51--67, \doi{10.1016/j.advengsoft.2016.01.008}.
	
	\bibitem[{MixesDB(2015)}]{mixesdb_2015-01-02_2015}
	MixesDB (2015): \enquote{2015-01-02 - {Floating} {Points} \& {Four} {Tet} @
		{Plastic} {People} {Closing} {Party}, {London}},
	\urlprefix\url{//www.mixesdb.com/w/2015-01-02_-_Floating_Points_%26_Four_Tet_@_Plastic_People_Closing_Party,_London} (Accessed: 20th March 2023).
	
	\bibitem[{MixesDB(2023)}]{mixesdb_main_2023}
	MixesDB (2023): \enquote{Main {Page}},
	\urlprefix\url{//www.mixesdb.com/w/Main_Page} (Accessed: 20th March 2023).
	
	\bibitem[{Moles(2019)}]{moles_sociodynamique_2019}
	Moles, A.~A. (2019): \textit{Sociodynamique de la culture}, Walter de Gruyter GmbH \& Co KG.
	
	\bibitem[{Morey(2013)}]{morey_copyright_2013}
	Morey, J. (2013): \enquote{Copyright {Management} and its {Effect} on the
		{Sampling} {Practice} of {UK} {Dance} {Music} {Producers}}, \textit{IASPM
		Journal}, 3(1), pp.\ignorespaces 48--62, \doi{10.5429/589}. Number: 1.
	
	\bibitem[{Naomi(2023)}]{naomi_spotify_2023}
	Naomi (2023): \enquote{Spotify {Debuts} a {New} {AI} {DJ}, {Right} in {Your}
		{Pocket}},
	\urlprefix\url{https://newsroom.spotify.com/2023-02-22/spotify-debuts-a-new-ai-dj-right-in-your-pocket/} (Accessed: 20th March 2023).
	
	\bibitem[{NTS(2023)}]{nts_2023}
	NTS (2023): \enquote{NTS Supporters},
	\urlprefix\url{https://www.nts.live/supporters} (Accessed: 20th March 2023).
	
	\bibitem[{Orio(2006)}]{orio_music_2006}
	Orio, N. (2006): "Music {Retrieval}: {A} {Tutorial} and {Review}",
	\textit{Foundations and Trends in Information Retrieval}, 1(1),
	pp.\ignorespaces 1--90, \doi{10.1561/1500000002}.
	
	\bibitem[{Partridge(2010)}]{partridge_dub_2010}
	Partridge, C. (2010): \textit{Dub in {Babylon}: understanding the evolution and
		significance of dub reggae in {Jamaica} and {Britain} from {King} {Tubby} to
		post-punk}, London: Equinox Pub.
	
	\bibitem[{Percival(2011)}]{percival_music_2011}
	Percival, J.~M. (2011): "Music {Radio} and the {Record} {Industry}:
		{Songs}, {Sounds}, and {Power}", \textit{Popular Music and Society}, 34(4),
	pp.\ignorespaces 455--473, \doi{10.1080/03007766.2011.601598}
	
	\bibitem[{Pinela(2017)}]{pinela_recommender_2017}
	Pinela, C. (2017): \enquote{Recommender {Systems} — {User}-{Based} and
		{Item}-{Based} {Collaborative} {Filtering}},
	\urlprefix\url{https://medium.com/@cfpinela/recommender-systems-user-based-and-item-based-collaborative-filtering-5d5f375a127f} (Accessed: 20th March 2023).
	
	\bibitem[{Porcaro et~al.(2021)Porcaro, Castillo, and
		Gómez}]{porcaro_diversity_2021}
	Porcaro, L., Castillo, C., and Gómez, E. (2021): "Diversity by
		{Design} in {Music} {Recommender} {Systems}", \textit{Transactions of the
		International Society for Music Information Retrieval}, 4(1),
	pp.\ignorespaces 114--126, \doi{10.5334/tismir.106}.
	
	\bibitem[{rekordbox(2020)}]{rekordbox_rekordbox_2020}
	rekordbox (2020): \enquote{rekordbox update (ver. 6.0.1) brings enhanced
		functions},
	\urlprefix\url{https://rekordbox.com/en/2020/05/rekordbox-update-ver-601/} (Accessed: 20th March 2023).
	
	\bibitem[{rekordbox(2023)}]{rekordbox_rekordbox_2023}
	rekordbox (2023): \enquote{rekordbox - {DJ} {Software}},
	\urlprefix\url{https://rekordbox.com/en/} (Accessed: 20th March 2023).
	
	\bibitem[{Rentfrow and Gosling(2003)}]{rentfrow_re_2003}
	Rentfrow, P.~J. and Gosling, S.~D. (2003): "The do re mi's of everyday
		life: {The} structure and personality correlates of music preferences",
	\textit{Journal of Personality and Social Psychology}, 84, pp.\ignorespaces
	1236--1256, \doi{10.1037/0022-3514.84.6.1236}
	
	\bibitem[{Reynolds(2013)}]{reynolds_energy_2013}
	Reynolds, S. (2013): \textit{Energy {Flash}: {A} {Journey} {Through} {Rave}
		{Music} and {Dance} {Culture}}. London: Faber \& Faber.
	
	\bibitem[{Ribecky et~al.(2021)Ribecky, Abeßer, and
		Lukashevich}]{ribecky_multi-input_2021}
	Ribecky, S., Abeßer, J., and Lukashevich, H. (2021): "Multi-input
		{Architecture} and {Disentangled} {Representation} {Learning} for
		{Multi}-dimensional {Modeling} of {Music} {Similarity}". \textit{arXiv preprint arXiv:2111.01710.}

	\bibitem[{Roberts(2020)}]{roberts_anti-spotify_2020}
	Roberts, R. (2020): \enquote{The anti-{Spotify}: {How} online music company
		{Bandcamp} became the toast of the {COVID} age},
	\urlprefix\url{https://www.latimes.com/entertainment-arts/music/story/2020-09-22/bandcamp-anti-spotify-streaming} (Accessed: 20th March 2023).

	\bibitem[{Robinson and Brown(2023)}]{robinson_automated_2023}
	Robinson, K. and Brown, D. (2023): "Automated {Time}-frequency {Domain}
		{Audio} {Crossfades} using {Graph} {Cuts}", \textit{arXiv preprint arXiv:2301.13380.}
	
	\bibitem[{Ronneberger et~al.(2015)Ronneberger, Fischer, and
		Brox}]{ronneberger_u-net_2015}
	Ronneberger, O., Fischer, P., and Brox, T. (2015): "U-{Net}:
		{Convolutional} {Networks} for {Biomedical} {Image} {Segmentation}", in \textit{Medical Image Computing and Computer-Assisted Intervention–MICCAI 2015: 18th International Conference}, Munich, Germany, October 5-9, 2015, Proceedings, Part III 18, pp. 234-241. \doi{10.48550/arXiv.1505.04597}
	
	\bibitem[{Sarwar et~al.(2001)Sarwar, Karypis, Konstan, and
		Riedl}]{sarwar_item-based_2001}
	Sarwar, B., Karypis, G., Konstan, J., and Riedl, J. (2001): "Item-based
		collaborative filtering recommendation algorithms", in \textit{Proceedings of
		the 10th international conference on {World} {Wide} {Web}}, Hong Kong, pp.\ignorespaces 285--295, \doi{10.1145/371920.372071}.
	
	\bibitem[{Saunders(2023)}]{saunders_soul_2023}
	Saunders, E. (2023): \enquote{De {La} {Soul}: {Classic} back catalogue finally
		available for streaming}, \urlprefix\url{https://www.bbc.co.uk/news/entertainment-arts-64152051} (Accessed: 20th March 2023).
	
	\bibitem[{Sgouros et~al.(2022)Sgouros, Bousis, and
		Mitianoudis}]{sgouros_efficient_2022}
	Sgouros, T., Bousis, A., and Mitianoudis, N. (2022): "An {Efficient}
		{Short}-{Time} {Discrete} {Cosine} {Transform} and {Attentive} {MultiResUNet}
		{Framework} for {Music} {Source} {Separation}", \textit{IEEE Access}, vol. 10,
	pp.\ignorespaces 119448--119459, \doi{10.1109/ACCESS.2022.3221766}.
	
	\bibitem[{Shardanand and Maes(1995)}]{shardanand_social_1995}
	Shardanand, U. and Maes, P. (1995): "Social information filtering:
		algorithms for automating “word of mouth”", in \textit{Proceedings of the
		{SIGCHI} conference on {Human} factors in computing systems},
	Denver, Colorado, United States, 1995. pp.\ignorespaces 210-217.
	\doi{10.1145/223904.223931}.
	
	\bibitem[{Sharma(2021)}]{sharma_audio_2021}
	Sharma, S. (2021): \enquote{Audio {Classification} {\textbar} {Introduction} to
		{Audio} {Classification}},
	\urlprefix\url{https://www.analyticsvidhya.com/blog/2021/06/introduction-to-audio-classification/} (Accessed: 20th March 2023).
	
	\bibitem[{Singh et~al.(2022)Singh, Sajid, Yadav, Singh, and
		Saini}]{singh_novel_2022}
	Singh, J., Sajid, M., Yadav, C.~S., Singh, S.~S., and Saini, M. (2022):
	"A {Novel} {Deep} {Neural}-based {Music} {Recommendation} {Method}
		considering {User} and {Song} {Data}", in \textit{2022 6th {International}
		{Conference} on {Trends} in {Electronics} and {Informatics} ({ICOEI})}, Tirunelveli, India, 2022, pp.\ignorespaces 1-7, \doi{10.1109/ICOEI53556.2022.9776660}.
	
	\bibitem[{Singh and Biswas(2022)}]{singh_robustness_2022}
	Singh, Y. and Biswas, A. (2022): "Robustness of musical features on
		deep learning models for music genre classification", \textit{Expert Systems
		with Applications}, 199, p.\ignorespaces 116879.
	\doi{10.1016/j.eswa.2022.116879}.
	
	\bibitem[{Spotify(2020{\natexlab{a}})}]{spotify_introducing_2020}
	Spotify (2020{\natexlab{a}}): \enquote{Introducing track {IDs}: {Co}-{Curated}
		{Playlists} {From} the {World}’s {Leading} {DJs}},
	\urlprefix\url{https://newsroom.spotify.com/2020-08-06/introducing-track-ids-co-curated-playlists-from-the-worlds-leading-djs/} (Accessed: 20th March 2023).
	
	\bibitem[{Spotify(2020{\natexlab{b}})}]{spotify_spotify_2020}
	Spotify (2020{\natexlab{b}}): \enquote{Spotify {Users} {Have} {Spent} {Over}
		2.3 {Billion} {Hours} {Streaming} {Discover} {Weekly} {Playlists} {Since}
		2015},
	\urlprefix\url{https://newsroom.spotify.com} (Accessed: 20th March 2023).
	
	\bibitem[{Spotify(2023)}]{spotify_web_2023}
	Spotify (2023): \enquote{Web {API} {Reference} {\textbar} {Spotify} for
		{Developers}},
	\urlprefix\url{https://developer.spotify.com/documentation/web-api/reference/} (Accessed: 20th March 2023).
	
	\bibitem[{Sturm(2014)}]{nurnberger_survey_2014}
	Sturm, B.~L. (2014): "A {Survey} of {Evaluation} in {Music} {Genre}
		{Recognition}", in \textit{Adaptive Multimedia Retrieval: Semantics, Context, and Adaptation: 10th International Workshop, AMR 2012}, Copenhagen, Denmark, October 24-25, 2012.
	pp.\ignorespaces 29-66. \doi{10.1007/978-3-319-12093-5_2}
	
	\bibitem[{Sánchez-Moreno et~al.(2018)Sánchez-Moreno, Zheng, and
		Moreno-García}]{sanchez-moreno_incorporating_2018}
	Sánchez-Moreno, D., Zheng, Y., and Moreno-García, M.~N. (2018):
	"Incorporating {Time} {Dynamics} and {Implicit} {Feedback} into
		{Music} {Recommender} {Systems}", in \textit{2018 {IEEE}/{WIC}/{ACM}
		{International} {Conference} on {Web} {Intelligence} ({WI})}.
	pp.\ignorespaces 580--585. \doi{10.1109/WI.2018.00-34}.
	
	\bibitem[{Takama et~al.(2021)Takama, Zhang, and
		Shibata}]{takama_context-aware_2021}
	Takama, Y., Zhang, J.-c., and Shibata, H. (2021): "Context-aware
		{Music} {Recommender} {System} {Based} on {Implicit} {Feedback}",
	\textit{Transactions of the Japanese Society for Artificial Intelligence},
	vol. 36(1). pp.\ignorespaces WI2--D\_1--10. \doi{10.1527/tjsai.36-1_WI2-D}.
	
	\bibitem[{Vall et~al.(2019)Vall, Dorfer, Eghbal-zadeh, Schedl, Burjorjee, and
		Widmer}]{vall_feature-combination_2019}
	Vall, A., Dorfer, M., Eghbal-zadeh, H., Schedl, M., Burjorjee, K., and Widmer,
	G. (2019): "Feature-combination hybrid recommender systems for
		automated music playlist continuation", \textit{User Modeling and
		User-Adapted Interaction}, 29(2). pp.\ignorespaces 527--572.
	\doi{10.1007/s11257-018-9215-8}.
	
	\bibitem[{Van~Meteren and Van~Someren(2000)}]{van_meteren_using_2000}
	Van~Meteren, R. and Van~Someren, M. (2000): "Using content-based
		filtering for recommendation", in \textit{Proceedings of the machine learning in the new information age}, Barcelona, vol.~30. pp.\ignorespaces 47-56.
	
	\bibitem[{Vlegels and Lievens(2017)}]{vlegels_music_2017}
	Vlegels, J. and Lievens, J. (2017): "Music classification, genres, and
		taste patterns: {A} ground-up network analysis on the clustering of artist
		preferences", \textit{Poetics}, 60. pp.\ignorespaces 76-89.
	\doi{10.1016/j.poetic.2016.08.004}.
	
	\bibitem[{Volkovs et~al.(2018)Volkovs, Rai, Cheng, Wu, Lu, and
		Sanner}]{volkovs_two-stage_2018}
	Volkovs, M., Rai, H., Cheng, Z., Wu, G., Lu, Y., and Sanner, S. (2018):
	"Two-stage {Model} for {Automatic} {Playlist} {Continuation} at
		{Scale}", in \textit{Proceedings of the {ACM} {Recommender} {Systems}
		{Challenge} 2018}, Vancouver, BC, Canada, 2nd October, 2018. pp.\ignorespaces 1--6,
	\doi{10.1145/3267471.3267480}.
	
	\bibitem[{Wang et~al.(2012)Wang, Rosenblum, and Wang}]{wang_context-aware_2012}
	Wang, X., Rosenblum, D., and Wang, Y. (2012): "Context-aware mobile
		music recommendation for daily activities", in \textit{Proceedings of the
		20th {ACM} international conference on {Multimedia}}, Nara Japan, 29th October - 2nd November 2012.
	pp.\ignorespaces 99--108, \doi{10.1145/2393347.2393368}.
	
	\bibitem[{Wheeler(2020)}]{wheeler_gentrification_2020}
	Wheeler, S. (2020): \enquote{The gentrification of jungle},
	\urlprefix\url{https://mixmag.net/feature/the-gentrification-of-jungle} (Accessed: 20th March 2023).
	
	\bibitem[{Yadav et~al.(2022)Yadav, Kumar~Singh, and Pal}]{yadav_improved_2022}
	Yadav, N., Kumar~Singh, A., and Pal, S. (2022): "Improved
		self-attentive {Musical} {Instrument} {Digital} {Interface} content-based
		music recommendation system", \textit{Computational Intelligence}, 38(4),
	pp.\ignorespaces 1232--1257, \doi{10.1111/coin.12501}.
	
	\bibitem[{Zamani et~al.(2019)Zamani, Schedl, Lamere, and
		Chen}]{zamani_analysis_2019}
	Zamani, H., Schedl, M., Lamere, P., and Chen, C.-W. (2019): "An
		{Analysis} of {Approaches} {Taken} in the {ACM} {RecSys} {Challenge} 2018 for
		{Automatic} {Music} {Playlist} {Continuation}", \textit{ACM Transactions on Intelligent Systems and Technology (TIST}), 10(5), pp.1-21.
	
	\bibitem[{Zhao and Wang(2022)}]{zhao_musical_2022}
	Zhao, Z. and Wang, H. (2022): "Musical {Instrument} {Classification}
		via {Low}-{Dimensional} {Feature} {Vectors}", \textit{arXiv preprint arXiv:1909.08444.}
	
	\bibitem[{Zheleva et~al.(2010)Zheleva, Guiver, Mendes~Rodrigues, and
		Milić-Frayling}]{zheleva_statistical_2010}
	Zheleva, E., Guiver, J., Mendes~Rodrigues, E., and Milić-Frayling, N. (2010):
	"Statistical models of music-listening sessions in social media", in
	\textit{Proceedings of the 19th international conference on {World} wide
		web}, New York, April 26-30, 2010. pp.\ignorespaces 1019--1028, \doi{10.1145/1772690.1772794}.
	
	\bibitem[{Zhou et~al.(2008)Zhou, Wilkinson, Schreiber, and
		Pan}]{zhou_large-scale_2008}
	Zhou, Y., Wilkinson, D., Schreiber, R., and Pan, R. (2008):
	"Large-{Scale} {Parallel} {Collaborative} {Filtering} for the
		{Netflix} {Prize}", in \textit{Algorithmic Aspects in Information and Management: 4th International Conference}, Shanghai, China, June 23-25, 2008. pp.\ignorespaces 337-348.
	\doi{10.1007/978-3-540-68880-8_32}.
	
	\bibitem[{Zhu et~al.(2021)Zhu, Niu, Fu, and Wang}]{zhu_musicbert_2021}
	Zhu, H., Niu, Y., Fu, D., and Wang, H. (2021): "{MusicBERT}: {A}
		{Self}-supervised {Learning} of {Music} {Representation}", in
	\textit{Proceedings of the 29th {ACM} {International} {Conference} on
		{Multimedia}}, New York, NY, USA, October 20-24, 2021. pp.\ignorespaces 3955-3963, \doi{10.1145/3474085.3475576}.
	
\end{thebibliography}


\end{document}
